---
title: "Cozmo emotion validation"
author: "Te-Yi Hsieh"
date: "02/03/2020"
output: html_document
---
###Experiment description
This is a online experiment which aims to validate people's emotional recognistion on Cozmo's emotional animations. Four targeted emotions - neutral, angry, sad, and happy expressions - are selected due to the interest of the second experiment of ECONOBOT project.

Index numbers of these four emotion categories are shown below:
- Neutral: 69, 91, 158, 169
- Angry: 55, 84, 130
- Sad: 59, 63, 134
- Happy: 103, 338, 348

###Setting Up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options("scipen"=10, "digits"=4)
```

###Loading in library
```{r library}
library(tidyverse)
```

###Loading in and tidy up datasets
```{r datasets}
#combine four .csv files
csv_files = list.files(pattern = "Result", full.names = TRUE)
csv_list = lapply(csv_files, read_csv)
Raw_data = do.call(rbind, csv_list)

#remove testing responses and whole-row NA
r_data <- Raw_data %>% filter(str_detect(feedback, "monkey") | str_detect(age, "monkey"))
Data <- anti_join(Raw_data, r_data, by = "session") %>% drop_na(6:17)

#sub-dataset: emotion category
dat_cat_num <- Data[ , 6:18] 

dat_cat <- dat_cat_num %>% gather("video", "reponse_num") %>%
  mutate(id = rep(c(1:64), 13), 
         response = case_when(reponse_num == 1 ~ "neutral",
            reponse_num == 2 ~ "happy",
            reponse_num == 3 ~ "sad",
            reponse_num == 4 ~ "angry",
            reponse_num == 5 ~ "other",
            reponse_num == 6 ~ "don't know")) 

#sub-dataset:emotion intensity
dat_int <- Data[ , 20:59] 
dat_int <- dat_int[ , -14]
```


###Participants' Demographics

The mean age for 64 participants is 27.6 years old. fourty three of them are female, 20 of them are male and one is gender variant.

```{r demographics}
#Age
age <- Data %>% summarise(age = mean(as.numeric(age), na.rm = TRUE))
age 

#Gender (gender options include: 1-female, 2-male, 3-Transgender female, 4-Transgender male, 5-Gender variant/ Non-conforming, 6-Prefer not to say)
gender <- Data %>% count(gender)
gender
```


##Accurate rate of recognising Cozmo's emotions

The emotion validation involves: 4 neutral, 3 happy, 3 sad, and 3 angry animations. Participants were asked to answer the emotion category and intensity they saw in each animation clip. The emotion category responses involes:
1. neutral
2. happy
3. sad
4. angry
5. other (can specify in text)
6. I don't know

###Neutral animation

There are four different neutral emotion animations used in the experiment.
```{r neutral}
#subsetting "Neutral" dataset
neurtal <- dat_cat[1:256, ]

#neutral animation (no.68)
neutral68 <- neurtal %>% subset(video == "Neutral68_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
neutral68

#neutral animation (no.91)
neutral91 <- neurtal %>% subset(video == "Neutral91_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
neutral91

#neutral animation (no.158)
neutral158 <- neurtal %>% subset(video == "Neutral158_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
neutral158

#neutral animation (no.169)
neutral169 <- neurtal %>% subset(video == "Neutral169_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
neutral169
```


###Angry animation

There are three different angry emotion animations used in the experiment.
```{r angry}
#subsetting "angry" dataset
angry <- dat_cat[257:448, ]

#angry animation (no.84)
angry84 <- angry %>% subset(video == "Angry84_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
angry84

#angry animation (no.55)
angry55 <- angry %>%  subset(video == "Angry55_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
angry55

#angry animation (no.130)
angry130 <- angry %>%  subset(video == "Angry130_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
angry130
```


###Happy animation

There are three different happy emotion animations used in the experiment.
```{r happy}
#subsetting "happy" dataset
happy <- dat_cat[449:640, ]

#happy animation (no.103)
happy103 <- happy %>% subset(video == "Happy103_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
happy103

#happy animation (no.338)
happy338 <- happy %>% subset(video == "Happy338_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
happy338

#happy animation (no.348)
happy348 <- happy %>% subset(video == "Happy348_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
happy348
```


###Sad animation

There are three different sad emotion animations used in the experiment.
```{r sad}
#subsetting "sad" dataset
sad <- dat_cat[641:832, ]

#sad animation (no.59)
sad59 <- sad %>% subset(video == "Sad59_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
sad59

#sad animation (no.63)
sad63 <- sad %>% subset(video == "Sad63_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
sad63

#sad animation (no.134)
sad134 <- sad %>% subset(video == "Sad134_type") %>% 
  count(response) %>% 
  mutate(resp_rate = n/64*100) %>%
  arrange(desc(resp_rate))
sad134
```



##Perceived emotional intensity of Cozmo's animations

The intensity analysis will focus on the rating of "correct" responses (e.g. For angry animantion, only the intensity of anger will be analysed)

###The emotional intensity of angry animation
```{r angry intensity}
angry_int <- dat_int %>% select(Angry55_intensity_Angry, Angry84_intensity_Angry, Angry130_intensity_Angry) %>%
  summarise(mAngry55 = mean(Angry55_intensity_Angry, na.rm = TRUE), 
         mAngry84 = mean(Angry84_intensity_Angry, na.rm = TRUE),
         mAngry130 = mean(Angry130_intensity_Angry, na.rm = TRUE))
angry_int
```


###The emotional intensity of happy animation
```{r happy intensity}
happy_int <- dat_int %>% select(Happy103_intensity_Happy, Happy338_intensity_Happy, Happy348_intensity_Happy) %>%
  summarise(mhappy103 = mean(Happy103_intensity_Happy, na.rm = TRUE), 
         mhappy338 = mean(Happy338_intensity_Happy, na.rm = TRUE),
         mhappy348 = mean(Happy348_intensity_Happy, na.rm = TRUE))
happy_int
```


###The emotional intensity of sad animation
```{r sad intensity}
sad_int <- dat_int %>% select(Sad59_intensity_Sad, Sad63_intensity_Sad, Sad134_intensity_Sad) %>%
  summarise(msad103 = mean(Sad59_intensity_Sad, na.rm = TRUE), 
         msad63 = mean(Sad63_intensity_Sad, na.rm = TRUE),
         msad134 = mean(Sad134_intensity_Sad, na.rm = TRUE))
sad_int
```

