---
title: "Cozmo emotion validation"
author: "Te-Yi Hsieh"
date: "02/03/2020"
output: html_document
---


###Setting Up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options("scipen"=10, "digits"=4)
```

###Loading in library
```{r library}
library(tidyverse)
```

###Loading in and tidy up datasets
```{r datasets}
#combine four .csv files
csv_files = list.files(pattern = "Result", full.names = TRUE)
csv_list = lapply(csv_files, read_csv)
Raw_data = do.call(rbind, csv_list)

#remove testing responses and whole-row NA
r_data <- Raw_data %>% filter(str_detect(feedback, "monkey") | str_detect(age, "monkey"))
Data <- anti_join(Raw_data, r_data, by = "session") %>% drop_na(6:17)
```


###Participants' Demographics

The mean age for 64 participants is 27.6 years old. fourty three of them are female, 20 of them are male and one is gender variant.

```{r demographics}
#Age
age <- Data %>% summarise(age = mean(as.numeric(age), na.rm = TRUE))
age 

#Gender (gender options include: 1-female, 2-male, 3-Transgender female, 4-Transgender male, 5-Gender variant/ Non-conforming, 6-Prefer not to say)
gender <- Data %>% count(gender)
gender
```


##Accuracy rate of recognising Cozmo's emotions

The emotion validation involves: 4 neutral, 3 happy, 3 sad, and 3 angry animations. Participants were asked to answer the emotion category and intensity they saw in each animation clip. The emotion category responses involes:
1. neutral
2. happy
3. sad
4. angry
5. other (can specify in text)
6. I don't know

###Neutral animation

There are four different neutral emotion animations used in the experiment.
```{r neutral}
#neutral animation (no.68)
neutral68 <- Data %>% count(Neutral68_type)
neutral68
```

